Scarid behavior GAM/GAMMS

### 2018-11-27 r/Models.Rmd
11/27

```{r}
pca_all <- prcomp(na.omit(sum_site %>% 
              remove_rownames %>% 
              column_to_rownames(var="site") %>%
              # filter(island!="Barbuda") %>%
              select(ma_cover, ma_canopy, ta_cover, ta_canopy, rugosity, scar_bm, scar_den)),
  center = T,scale = T)
autoplot(pca_all, data = sum_site, colour = 'island',
         # frame = T, frame.type = "norm",
         loadings = T, loadings.colour = 'gray',
         loadings.label = T, loadings.label.size = 3, loadings.label.colour = 'black',
            loadings.label.repel = T) +
    scale_color_manual(name="island", values=c("lightblue", "darkseagreen", "salmon")) + 
    theme(legend.direction = 'horizontal', legend.position = 'top') +
    theme_minimal()

@@

>>>>

```{r}
pca_all <- prcomp(na.omit(sum_site %>% 
              remove_rownames %>% 
              column_to_rownames(var="site") %>%
              # filter(island!="Barbuda") %>%
              select(ma_cover, ma_canopy, ta_cover, ta_canopy, rugosity, scar_bm, scar_den, lc_cover, carn30_bm)),
  center = T,scale = T)
autoplot(pca_all, data = sum_site, colour = 'island',
         # frame = T, frame.type = "norm",
         loadings = T, loadings.colour = 'gray',
         loadings.label = T, loadings.label.size = 3, loadings.label.colour = 'black',
            loadings.label.repel = T) +
    scale_color_manual(name="island", values=c("lightblue", "darkseagreen", "salmon")) + 
    theme(legend.direction = 'horizontal', legend.position = 'top') +
    theme_minimal()

@@

Site-level GAMM with pca_all
```{r}
m_data <- sum_ssp_pca %>% filter(species_code!="rbp")

# Main effects only
gamm1 <- gamm(fr_mean ~ species_code + s(length_m) + phase + s(pc1_all) + s(pc2_all), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
summary(gamm1$gam)
plot(gamm1$gam,pages=1)
plot(gamm1$lme) # not too heteroskedastic?
AIC(gamm1$lme)

# Interactions
gamm2 <- gamm(fr_mean ~ species_code + phase + s(length_m, by = factor(species_code)) + s(pc2_all)  + s(pc1_all, by = factor(species_code)), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
summary(gamm2$gam)
plot(gamm2$gam,pages=1)
plot(gamm2$lme) # not too heteroskedastic?
AIC(gamm2$lme)
# Slightly significant interaction between pc1_all and species_code=qup, but this has lower R2 than model with all main effects
# length/species and pc2/species interactions were not significant

# Reducing non-significant effects
gamm3 <- gamm(fr_mean ~ species_code + phase + s(pc1_all) + s(pc2_all), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
summary(gamm3$gam)
plot(gamm3$gam,pages=1)
plot(gamm3$lme) # not too heteroskedastic?
AIC(gamm3$lme)

# Adding pc1/species interaction back in to model with streamlined main effects
gamm4 <- gamm(fr_mean ~ species_code + phase + s(pc1_all, by = factor(species_code)), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
summary(gamm4$gam)
plot(gamm4$gam,pages=1)
plot(gamm4$lme) # not too heteroskedastic?
AIC(gamm4$lme)
